---
title: "eds-212-day2-handout"
---

```{r}
library(tidyverse)
library(palmerpenguins)
```

1.  Find the slope of f(x)= x \^ 2 , x = 3

    ```{r}
    fx = expression( x ^ 2)
    x = 3
    D = D(fx, 'x')
    eval(D)
    ```

2.  Find the slope of P(a)= 2(3a+2)^4−5, a=1.2

    ```{r}
    ax = expression(2 * (3 * a + 2) ^ 4 - 5)
    a = 1.2
    dax = D(ax, 'a')
    eval(dax)
    ```

3.  Let's create a penguin plot create a `ggplot` graph of penguin bill length versus bill depth (using the `penguins` dataset in the `palmerpenguins` package), with point color dependent on species. You should attach the `tidyverse` and `palmerpenguins` package in your .qmd setup chunk if you haven\'t already. Update labels and add a title.

    ```{r}
    ggplot(data = penguins, aes(x = penguins$bill_length_mm, y = penguins$bill_depth_mm, color = species)) + geom_point() + labs(x = "Bill Length in MM", y = "Bill Depth in MM", title = "Penguin Size in Length and Width by Species")
    ```

```{r}
ggplot(data = penguins, aes(x = penguins$species, y = penguins$flipper_length_mm)) + geom_jitter() + labs(x = "Species", y = "Flipper Length in MM", title = "Penguin Flipper Size by Species")
```
